Titeltext

### 2018-07-26 thesis/paper/paper.tex
Added allowed units

>>>>

\subsection{Allowed units (Q21514353)}
The allowed units constraint specifies that a constrained statement may only have a unit that is in a set of specific units.

\begin{table}[H]
\caption{Conflicts-with constraint (Q21502838)}
\begin{tabularx}{\textwidth}{ ll X}
\hline
Requirement & constrained statement unit \\
\hline
Qualifiers & \makecell{allowed unit (P2305) -- 1..* \\ units that the statement may have (or none for dimensionless units)} \\
\hline
Violation & \makecell{constrained statement with a unit unequal to all allowed units} \\
\hline
Dependency & constrained statement and its unit \\
\hline
Rule features & inequality \\
\hline
\end{tabularx}
\end{table}

Modelling the constraint requires a predicate associating the value or the statement with its unit and inequality between every unit and all allowed units. Then a violation can be found by finding all tripleEDB with the constrained property and a unit unequal to all allowed units.
